An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-31 VLDB2026/main.tex
1

	\textit{\textbf{\textcolor{red}{Large-scale Dataset.}}} \textcolor{red}{As shown in the Figure~\ref{fig: range big dataset}, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged. However, their high performance is achieved at the cost of extremely high memory consumption (Figure~\ref{fig:rangeFilter_search_memory_mb}). In contrast, VBASE and Faiss demonstrate moderate performance while consuming significantly less memory.}

%	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Range}}
	\section{DISCUSSION}
	Based on the performance of the algorithms on different experimental scenarios, we discuss our findings as follows.

@@

\begin{table*}[htbp]
	\caption{Algorithm Recommendation}
	\resizebox{\textwidth}{!}{
\begin{tabular}{|l|*{16}{c|}}
	\hline
	\multirow{2}{*}{\textbf{Application Scenarios / Algorithms}} 
	& \multicolumn{6}{c|}{\textbf{AF}} 
	& \multicolumn{5}{c|}{\textbf{RF}} 
	& \multicolumn{5}{c|}{\textbf{AF / RF}} \\
	\cline{2-17}
	& \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS}  & \textbf{UNG} & \textbf{Puck} 
	& \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win} 
	& \textbf{ACORN}& \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
	\hline
	\textbf{Query Performance} & S & M & S & M &\textbf{S} & S & M & M & W & M & S & M/M & M/M & M/M & W/W & W/W \\
	\textbf{Index Time} &M  &M  &M  &M  &M  &S  &W  &M  &S  &W  &W  &W/W &\textbf{S}/\textbf{S} &S/S  &W/M  &W/W  \\
	\textbf{Peak Memory} &W  &M  &M  &M  &M  &S  &W  &W  &M  &W  &W  &W/W  &\textbf{S}/\textbf{S}  &S/M  &S/M  &S/S \\
	\textbf{Large-Scale Dataset} & S & S & W & W &\textbf{S} &S  &M  &S  &M  &S  &\textbf{S}  &M/W  &W/M  &W/W  &M/M  &-  \\
	\textbf{Rare Attribute \& Low Range} &M  &M  &S  &S &\textbf{S}  &S  &S  &S  &W  &M  &\textbf{S} &M/M  &M/M  &W/W  &W/W  &W/W  \\
	\textbf{Robust to Multi-Modal Dataset} &S  &S  &W  &S  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &M/M  &W/M  &W/W  &W/W  &W/W  \\
	\textbf{Robust to Attribute Distribution} &W  &W  &S  &S  &S  &S  &-  &-  &-  &-  &-  &S/-  &W/-  &\textbf{S}/-  &W/-  &W/-  \\
	\textbf{High LID Dataset} &S  &M  &S  &M  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &W/W  &M/S  &W/W  &W/M  &W/W  \\
	\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faTimes &\faTimes  & \faCheck &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faCheck&\faTimes  \\
	\hline
\end{tabular}
	}
	\vspace{1mm}
\begin{flushleft}
	\textbf{Performance Levels:} \quad \textbf{S} = Strongest, S = Strong, M = Medium, W = Weak, - = Not Supported \\
	\textbf{Recommendation:} \quad \faCheck = Recommended, \faTimes = Not Recommended
\end{flushleft}
	\centering

@@

\textcolor{red}{
Faiss, Milvus and VBASE effectively handle complex filtering by employing versatile "pre-filtering" or "post-filtering" strategies, granting them significant flexibility and broad applicability. This flexibility, however, is often counterbalanced by their relatively modest overall search performance. Relatively speaking, PASE performs less well across various aspects, which indicates that its strategy of loading data pages on-demand is unsuitable for performance-demanding scenarios.}

>>>>

	\textit{\textbf{\textcolor{red}{Large-scale Dataset.}}} \textcolor{red}{As shown in the figure~\ref{fig: range big dataset}, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged. However, their high performance is achieved at the cost of extremely high memory consumption (Figure~\ref{fig:rangeFilter_search_memory_mb}). In contrast, VBASE and Faiss demonstrate moderate performance while consuming significantly less memory.}

%	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Range}}
	\section{DISCUSSION}
	\textcolor{orange}{Based on the performance of algorithms across various experimental settings, we evaluate their strengths and weaknesses in different application scenarios, as shown in Table \ref{tab:algorithm_recommendation}. Next, we provide a detailed discussion of the advantages and disadvantages of each algorithm.}

@@

\begin{table*}[htbp]
	\caption{Algorithm Recommendation}
	\label{tab:algorithm_recommendation}
	\resizebox{\textwidth}{!}{

\begin{tabular}{|l|*{16}{c|}}
	\hline
	\multirow{2}{*}{\textbf{Application Scenarios / Algorithms}} 
	& \multicolumn{6}{c|}{\textbf{AF}} 
	& \multicolumn{5}{c|}{\textbf{RF}} 
	& \multicolumn{5}{c|}{\textbf{AF / RF}} \\
	\cline{2-17}
	& \textbf{UNG} & \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS} & \textbf{Puck} 
	& \textbf{Win} & \textbf{iRange} & \textbf{SeRF} & \textbf{DSG} & \textbf{UNIFY} 
	& \textbf{ACORN} & \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
	\hline
	\textbf{Performance Critical} & \textbf{B} & G & M & G & M & G & G & M & P & M & M & M/M & M/M & M/M & P/P & P/P \\
	\textbf{Fast Index Construction} & M & M & M & M & M & G & P & M & G & P & P & P/P & \textbf{B}/\textbf{B} & G/G & P/M & P/P \\
	\textbf{Memory Constraint} & M & P & M & M & M & G & P & P & M & P & P & P/P & \textbf{B}/\textbf{B} & G/M & G/M & G/G \\
	\textbf{Large-Scale Dataset} & \textbf{B} & G & G & P & P & G & \textbf{B} & G & M & M & G & M/P & P/M & P/P & M/M & - \\
	\textbf{Multi-Modal Dataset} & \textbf{B} & G & G & P & G & M & \textbf{B} & G & M & M & G & M/M & P/M & P/P & P/P & P/P \\
	\textbf{High LID Dataset} & \textbf{B} & G & M & G & M & M & \textbf{B} & G & M & M & G & P/P & M/G & P/P & P/M & P/P \\
	\textbf{Rare Attribute \& Low Range} & \textbf{B} & P & M & G & G & G & \textbf{B} & G & P & G & M & M/M & M/M & P/P & P/P & P/P \\
	\textbf{Robust to Attribute Distribution} & G & P & P & G & G & G & - & - & - & - & - & G/- & P/- & \textbf{B}/- & P/- & P/- \\
	\textbf{General-Purpose} & G & G & G & P & P & P & G & P & P & P & G & P & G & G & G & P \\
	\hline
\end{tabular}

	}
	\vspace{1mm}
\begin{flushleft}
	\textbf{Performance Levels:} \quad B = Best, G = Good , M = Moderate, P = Poor, - = Not Supported \\
\end{flushleft}
	\centering

@@

\textcolor{red}{
Faiss, Milvus and VBASE effectively handle complex filtering by employing versatile "pre-filtering" or "post-filtering" strategies, granting them significant flexibility and broad applicability. This flexibility, however, is often counterbalanced by their relatively modest overall search performance. Relatively speaking, PASE performs less well across various aspects.}
